#rm(list=ls())
#Read Data
```{r}
Agartala <- read.csv('api_data_IN_Agartala_raw.csv', head = TRUE)
Agra <- read.csv('api_data_IN_Agra_raw.csv', head = TRUE)
Aizwal <- read.csv('api_data_IN_Aizwal_raw.csv', head = TRUE)
Amritsar <- read.csv('api_data_IN_Amritsar_raw.csv', head = TRUE)
Asansol <- read.csv('api_data_IN_Asansol_raw.csv', head = TRUE)
Aurangabad <- read.csv('api_data_IN_Aurangabad_raw.csv', head = TRUE)
Bareilly <- read.csv('api_data_IN_Bareilly_raw.csv', head = TRUE)
Belgaum <- read.csv('api_data_IN_Belgaum_raw.csv', head = TRUE)
Bengaluru <- read.csv('api_data_IN_Bengaluru_raw.csv', head = TRUE)
Bhilai <- read.csv('api_data_IN_Bhilai_raw.csv', head = TRUE)
Bhopal <- read.csv('api_data_IN_Bhopal_raw.csv', head = TRUE)
Chandigarh<- read.csv('api_data_IN_Chandigarh_raw.csv', head = TRUE)
Chennai <- read.csv('api_data_IN_Chennai_raw.csv', head = TRUE)
Coimbatore <- read.csv('api_data_IN_Coimbatore_raw.csv', head = TRUE)
Dehradun <- read.csv('api_data_IN_Dehradun_raw.csv', head = TRUE)
Delhi <- read.csv('api_data_IN_Delhi_raw.csv', head = TRUE)
Faridabad <- read.csv('api_data_IN_Faridabad_raw.csv', head = TRUE)
Gandhinagar<- read.csv('api_data_IN_Gandhinagar_raw.csv', head = TRUE)
Gangtok <- read.csv('api_data_IN_Gangtok_raw.csv', head = TRUE)
Ghaziabad <- read.csv('api_data_IN_Ghaziabad_raw.csv', head = TRUE)
Gorakhpur <- read.csv('api_data_IN_Gorakhpur_raw.csv', head = TRUE)
Gwalior <- read.csv('api_data_IN_Gwalior_raw.csv', head = TRUE)
Hyderabad <- read.csv('api_data_IN_Hyderabad_raw.csv', head = TRUE)
Imphal <- read.csv('api_data_IN_Imphal_raw.csv', head = TRUE)
Indore<- read.csv('api_data_IN_Indore_raw.csv', head = TRUE)
Jabalpur <- read.csv('api_data_IN_Jabalpur_raw.csv', head = TRUE)
Jaipur <- read.csv('api_data_IN_Jaipur_raw.csv', head = TRUE)
Jalandhar <- read.csv('api_data_IN_Jalandhar_raw.csv', head = TRUE)
Jodhpur<- read.csv('api_data_IN_Jodhpur_raw.csv', head = TRUE)
Kanpur <- read.csv('api_data_IN_Kanpur_raw.csv', head = TRUE)
Kochi <- read.csv('api_data_IN_Kochi_raw.csv', head = TRUE)
Kohima<- read.csv('api_data_IN_Kohima_raw.csv', head = TRUE)
Kolkata <- read.csv('api_data_IN_Kolkata_raw.csv', head = TRUE)
Kota <- read.csv('api_data_IN_Kota_raw.csv', head = TRUE)
Kozhikode <- read.csv('api_data_IN_Kozhikode_raw.csv', head = TRUE)
Lucknow <- read.csv('api_data_IN_Lucknow_raw.csv', head = TRUE)
Ludhiana <- read.csv('api_data_IN_Ludhiana_raw.csv', head = TRUE)
Mangalore <- read.csv('api_data_IN_Mangalore_raw.csv', head = TRUE)
Meerut <- read.csv('api_data_IN_Meerut_raw.csv', head = TRUE)
Moradabad <- read.csv('api_data_IN_Moradabad_raw.csv', head = TRUE)
Mumbai <- read.csv('api_data_IN_Mumbai_raw.csv', head = TRUE)
Mysuru <- read.csv('api_data_IN_Mysuru_raw.csv', head = TRUE)
Nashik <- read.csv('api_data_IN_Nashik_raw.csv', head = TRUE)
Patna <- read.csv('api_data_IN_Patna_raw.csv', head = TRUE)
Prayagraj <- read.csv('api_data_IN_Prayagraj_raw.csv', head = TRUE)
Puducherry <- read.csv('api_data_IN_Puducherry_raw.csv', head = TRUE)
Pune<- read.csv('api_data_IN_Pune_raw.csv', head = TRUE)
Shillong <- read.csv('api_data_IN_Shillong_raw.csv', head = TRUE)
Solapur <- read.csv('api_data_IN_Solapur_raw.csv', head = TRUE)
Srinagar <- read.csv('api_data_IN_Srinagar_raw.csv', head = TRUE)
Thiruvananthapuram <- read.csv('api_data_IN_Thiruvananthapuram_raw.csv', head = TRUE)
Varanasi <- read.csv('api_data_IN_Varanasi_raw.csv', head = TRUE)
Vijaywada <- read.csv('api_data_IN_Vijaywada_raw.csv', head = TRUE)
Visakhapatnam <- read.csv('api_data_IN_Visakhapatnam_raw.csv', head = TRUE)
```


#Get Lat and Long for each City
```{r}
Agartala_latlong <- Agartala[1,2:4]
Agra_latlong <- Agra[1,2:4]
Aizwal_latlong <- Aizwal[1,2:4]
Amritsar_latlong <- Amritsar[1,2:4]
Asansol_latlong <- Asansol[1,2:4]
Aurangabad_latlong <-Aurangabad[1,2:4]
Bareilly_latlong <- Bareilly[1,2:4]
Belgaum_latlong <- Belgaum[1,2:4]
Bengaluru_latlong <- Bengaluru[1,2:4]
Bhilai_latlong <- Bhilai[1,2:4]
Bhopal_latlong <- Bhopal[1,2:4]
Chandigarh_latlong<- Chandigarh[1,2:4] 
Chennai_latlong <- Chennai[1,2:4]
Coimbatore_latlong <- Coimbatore[1,2:4]
Dehradun_latlong <-Dehradun[1,2:4]
Delhi_latlong <- Delhi[1,2:4]
Faridabad_latlong <- Faridabad[1,2:4]
Gandhinagar_latlong<-Gandhinagar[1,2:4]
Gangtok_latlong <- Gangtok[1,2:4]
Ghaziabad_latlong <- Ghaziabad[1,2:4]
Gorakhpur_latlong <- Gorakhpur[1,2:4]
Gwalior_latlong <- Gwalior[1,2:4]
Hyderabad_latlong <- Hyderabad[1,2:4]
Imphal_latlong <- Imphal[1,2:4]
Indore_latlong<- Indore[1,2:4]
Jabalpur_latlong <- Jabalpur[1,2:4]
Jaipur_latlong <- Jaipur[1,2:4]
Jalandhar_latlong <-Jalandhar[1,2:4]
Jodhpur_latlong<-Jodhpur[1,2:4]
Kanpur_latlong <- Kanpur[1,2:4]
Kochi_latlong <- Kochi[1,2:4]
Kohima_latlong<- Kohima[1,2:4]
Kolkata_latlong <- Kolkata[1,2:4]
Kota_latlong <- Kota[1,2:4]
Kozhikode_latlong <-Kozhikode[1,2:4]
Lucknow_latlong <-Lucknow[1,2:4]
Ludhiana_latlong <- Ludhiana[1,2:4]
Mangalore_latlong <- Mangalore[1,2:4]
Meerut_latlong <- Meerut[1,2:4]
Moradabad_latlong <- Moradabad[1,2:4]
Mumbai_latlong <- Mumbai[1,2:4]
Mysuru_latlong <- Mysuru[1,2:4]
Nashik_latlong <- Nashik[1,2:4]
Patna_latlong <- Patna[1,2:4]
Prayagraj_latlong <- Prayagraj[1,2:4]
Puducherry_latlong <- Puducherry[1,2:4]
Pune_latlong<- Pune[1,2:4]
Shillong_latlong <- Shillong[1,2:4]
Solapur_latlong <- Solapur[1,2:4]
Srinagar_latlong <- Srinagar[1,2:4]
Thiruvananthapuram_latlong <- Thiruvananthapuram[1,2:4]
Varanasi_latlong <- Varanasi[1,2:4]
Vijaywada_latlong <- Vijaywada[1,2:4]
Visakhapatnam_latlong <- Visakhapatnam[1,2:4]
```

#Merge Rows
```{r}
df <- Agartala_latlong
df[nrow(df) + 1,] <- Agra_latlong
df[nrow(df) + 1,] <- Aizwal_latlong
df[nrow(df) + 1,] <- Amritsar_latlong 
df[nrow(df) + 1,] <- Asansol_latlong 
df[nrow(df) + 1,] <- Aurangabad_latlong
df[nrow(df) + 1,] <- Bareilly_latlong
df[nrow(df) + 1,] <- Belgaum_latlong
df[nrow(df) + 1,] <- Bengaluru_latlong
df[nrow(df) + 1,] <- Bhilai_latlong
df[nrow(df) + 1,] <- Bhopal_latlong
df[nrow(df) + 1,] <-Chandigarh_latlong
df[nrow(df) + 1,] <-Chennai_latlong
df[nrow(df) + 1,] <-Coimbatore_latlong
df[nrow(df) + 1,] <-Dehradun_latlong
df[nrow(df) + 1,] <-Delhi_latlong
df[nrow(df) + 1,] <-Faridabad_latlong
df[nrow(df) + 1,] <-Gandhinagar_latlong
df[nrow(df) + 1,] <-Gangtok_latlong
df[nrow(df) + 1,] <- Ghaziabad_latlong
df[nrow(df) + 1,] <-Gorakhpur_latlong
df[nrow(df) + 1,] <-Gwalior_latlong
df[nrow(df) + 1,] <-Hyderabad_latlong
df[nrow(df) + 1,] <-Imphal_latlong
df[nrow(df) + 1,] <-Indore_latlong
df[nrow(df) + 1,] <-Jabalpur_latlong
df[nrow(df) + 1,] <- Jaipur_latlong
df[nrow(df) + 1,] <-Jalandhar_latlong
df[nrow(df) + 1,] <- Jodhpur_latlong
df[nrow(df) + 1,] <-Kanpur_latlong
df[nrow(df) + 1,] <-Kochi_latlong
df[nrow(df) + 1,] <-Kohima_latlong
df[nrow(df) + 1,] <-Kolkata_latlong
df[nrow(df) + 1,] <-Kota_latlong
df[nrow(df) + 1,] <- Kozhikode_latlong
df[nrow(df) + 1,] <- Lucknow_latlong
df[nrow(df) + 1,] <-Ludhiana_latlong
df[nrow(df) + 1,] <-Mangalore_latlong
df[nrow(df) + 1,] <-Meerut_latlong
df[nrow(df) + 1,] <-Moradabad_latlong
df[nrow(df) + 1,] <-Mumbai_latlong
df[nrow(df) + 1,] <-Mysuru_latlong
df[nrow(df) + 1,] <-Nashik_latlong
df[nrow(df) + 1,] <-Patna_latlong
df[nrow(df) + 1,] <-Prayagraj_latlong
df[nrow(df) + 1,] <-Puducherry_latlong
df[nrow(df) + 1,] <-Pune_latlong
df[nrow(df) + 1,] <-Shillong_latlong
df[nrow(df) + 1,] <-Solapur_latlong
df[nrow(df) + 1,] <-Srinagar_latlong
df[nrow(df) + 1,] <-Thiruvananthapuram_latlong
df[nrow(df) + 1,] <-Varanasi_latlong
df[nrow(df) + 1,] <-Vijaywada_latlong
df[nrow(df) + 1,] <- Visakhapatnam_latlong
```

#Assign Clusters
```{r}

#Savannah             1
#Steppe and Desert    2
#Humid Subtropical    3
#Mediterran           4
#Oceanic Subtropical Highland             5
#Monsoon              6
#Marine West Coast    7

clusters <- c('Savannah','Desert','Subtropical','Subtropical','Savannah','Desert','Subtropical','Savannah','Savannah','Savannah','Mediterran','Subtropical','Savannah','Savannah','Subtropical','Subtropical','Desert','Desert','Oceanic Subtropical Highland','Subtropical','Subtropical','Mediterran','Savannah','Subtropical','Savannah','Mediterran','Desert','Subtropical','Desert','Mediterran','Monsoon', 'Oceanic Subtropical Highland','Savannah','Desert','Monsoon','Mediterran','Subtropical','Savannah','Subtropical','Subtropical','Savannah','Savannah','Savannah','Subtropical','Savannah','Mediterran','Savannah','Subtropical','Desert','Marine West Coast','Monsoon','Subtropical','Savannah','Savannah')

df$Cluster <- cbind(df, clusters)

```

#Export CSV
```{r}
write.csv(df,"cluster2.csv")
```


#Read New CSV
```{r}
df <- read.csv('cluster.csv', head = TRUE)
```



#Create df based on climate cluster
```{r}
sav <- df[df$Cluster.Name == 'Savannah',]
desert <- df[df$Cluster.Name == 'Desert',] 
subtrop <- df[df$Cluster.Name == 'Subtropical',] 
med <- df[df$Cluster.Name == 'Mediterran',] 
highland <- df[df$Cluster.Name == 'Oceanic Subtropical Highland',] 
monsoon <- df[df$Cluster.Name == 'Monsoon',] 

```

#Combine Weather Data for Each Group
```{r}
#Savannah
sav_city <- sav$City
df_sav <- rbind(Agartala,Asansol,Belgaum,Bengaluru,Bhilai,Chennai,Coimbatore,Hyderabad,Indore,Kolkata,Mangalore,Mumbai,Mysuru,Nashik,Prayagraj,Puducherry,Pune,Vijaywada,Visakhapatnam)

#Desert
desert_city <- desert$City
df_desert <- rbind(Agra,Aurangabad,Faridabad,Gandhinagar,Jaipur,Jodhpur,Kota,Solapur)

#Subtropical
subtrop_city <- subtrop$City
df_subtrop <- rbind(Aizwal,Amritsar,Bareilly,Chandigarh,Dehradun,Delhi,Ghaziabad,Gorakhpur,Imphal,Jalandhar,Ludhiana,Meerut,Moradabad,Patna,Shillong,Srinagar,Varanasi)

#Mediterran
med_city <- med$City
df_med <- rbind(Bhopal,Gwalior,Jabalpur,Kanpur,Lucknow)

#Oceanic Highland
highland_city <- highland$City
df_highland <- rbind(Gangtok,Kohima)

#Monsoon
monsoon_city <- monsoon$City
df_monsoon <- rbind(Kochi, Kozhikode, Thiruvananthapuram)
```

#Plot Time series for each cluster by pollutant
#Savannah
#CO
```{r}
ts.plot(Agartala$CO, main='Agartala')
ts.plot(Asansol$CO, main='Asansol')
ts.plot(Belgaum$CO, main='Belgaum')
ts.plot(Bengaluru$CO, main='Bengaluru')
ts.plot(Bhilai$CO, main='Bhilai')
ts.plot(Chennai$CO, main='Chennai')
ts.plot(Coimbatore$CO, main='Coimbatore')
ts.plot(Hyderabad$CO, main='Hyderabad')
ts.plot(Indore$CO, main='Indore')
ts.plot(Kolkata$CO, main='Kolkata')
ts.plot(Mangalore$CO, main='Mangalore')
ts.plot(Mumbai$CO, main='Mumbai')
ts.plot(Mysuru$CO, main='Mysuru')
ts.plot(Nashik$CO, main='Nashik')
ts.plot(Prayagraj$CO, main='Prayagraj')
ts.plot(Puducherry$CO, main='Puducherry')
ts.plot(Pune$CO, main='Pune')
ts.plot(Vijaywada$CO, main='Vijaywada')
ts.plot(Visakhapatnam$CO, main='Visakhapatnam')

#Trend plot for Pune
pune.ts <- ts(Pune$CO, start=2020, freq=365)
time.pts <- c(1:length(pune.ts))
time.pts= c(time.pts- min(time.pts))/max(time.pts)

##Splines Method for Trend Estimation
gam.fit.co = gam(pune.ts~s(time.pts))
pune.co.fit.gam = ts(fitted(gam.fit.co), start=2020, freq=365)

ts.plot(pune.ts,ylab="CO", main="CO Trend")
lines(pune.co.fit.gam,lwd=2,col="red")

#Mumbai - still good but has high spikes in the typical drop period
#Not like the others: Asansol, Puducherry, Visakhapatnam
```
#NO2
```{r}
ts.plot(Agartala$NO2, main='Agartala')
ts.plot(Asansol$NO2, main='Asansol')
ts.plot(Belgaum$NO2, main='Belgaum')
ts.plot(Bengaluru$NO2, main='Bengaluru')
ts.plot(Bhilai$NO2, main='Bhilai')
ts.plot(Chennai$NO2, main='Chennai')
ts.plot(Coimbatore$NO2, main='Coimbatore')
ts.plot(Hyderabad$NO2, main='Hyderabad')
ts.plot(Indore$NO2, main='Indore')
ts.plot(Kolkata$NO2, main='Kolkata')
ts.plot(Mangalore$NO2, main='Mangalore')
ts.plot(Mumbai$NO2, main='Mumbai')
ts.plot(Mysuru$NO2, main='Mysuru')
ts.plot(Nashik$NO2, main='Nashik')
ts.plot(Prayagraj$NO2, main='Prayagraj')
ts.plot(Puducherry$NO2, main='Puducherry')
ts.plot(Pune$NO2, main='Pune')
ts.plot(Vijaywada$NO2, main='Vijaywada')
ts.plot(Visakhapatnam$NO2, main='Visakhapatnam')

#Trend plot for Pune
pune.ts <- ts(Pune$NO2, start=2020, freq=365)
time.pts <- c(1:length(pune.ts))
time.pts= c(time.pts- min(time.pts))/max(time.pts)

##Splines Method for Trend Estimation
gam.fit.no = gam(pune.ts~s(time.pts))
pune.no.fit.gam = ts(fitted(gam.fit.no), start=2020, freq=365)

ts.plot(pune.ts,ylab="NO2", main="NO2 Trend")
lines(pune.no.fit.gam,lwd=2,col="red")


#Not like the others: Asansol, Bengaluru, Bhilai, Chennai, Mangalore, Mumbai, Nashik, Puducherry, Visakhapatnam
```



#SO2
```{r}
ts.plot(Agartala$SO2, main='Agartala')
ts.plot(Asansol$SO2, main='Asansol')
ts.plot(Belgaum$SO2, main='Belgaum')
ts.plot(Bengaluru$SO2, main='Bengaluru')
ts.plot(Bhilai$SO2, main='Bhilai')
ts.plot(Chennai$SO2, main='Chennai')
ts.plot(Coimbatore$SO2, main='Coimbatore')
ts.plot(Hyderabad$SO2, main='Hyderabad')
ts.plot(Indore$SO2, main='Indore')
ts.plot(Kolkata$SO2, main='Kolkata')
ts.plot(Mangalore$SO2, main='Mangalore')
ts.plot(Mumbai$SO2, main='Mumbai')
ts.plot(Mysuru$SO2, main='Mysuru')
ts.plot(Nashik$SO2, main='Nashik')
ts.plot(Prayagraj$SO2, main='Prayagraj')
ts.plot(Puducherry$SO2, main='Puducherry')
ts.plot(Pune$SO2, main='Pune')
ts.plot(Vijaywada$SO2, main='Vijaywada')
ts.plot(Visakhapatnam$SO2, main='Visakhapatnam')

#Trend plot for Pune
pune.ts <- ts(Pune$SO2, start=2020, freq=365)
time.pts <- c(1:length(pune.ts))
time.pts= c(time.pts- min(time.pts))/max(time.pts)

##Splines Method for Trend Estimation
gam.fit.so = gam(pune.ts~s(time.pts))
pune.so.fit.gam = ts(fitted(gam.fit.so), start=2020, freq=365)

ts.plot(pune.ts,ylab="SO2", main="SO2 Trend")
lines(pune.so.fit.gam,lwd=2,col="red")

#Not like the others: Asansol, Bhilai, Chennai, Mangalore, Mumbai, Nashik, Puducherry,Visakhapatnam
```



#PM
```{r}
ts.plot(Agartala$PM2_5, main='Agartala')
ts.plot(Asansol$PM2_5, main='Asansol')
ts.plot(Belgaum$PM2_5, main='Belgaum')
ts.plot(Bengaluru$PM2_5, main='Bengaluru')
ts.plot(Bhilai$PM2_5, main='Bhilai')
ts.plot(Chennai$PM2_5, main='Chennai')
ts.plot(Coimbatore$PM2_5, main='Coimbatore')
ts.plot(Hyderabad$PM2_5, main='Hyderabad')
ts.plot(Indore$PM2_5, main='Indore')
ts.plot(Kolkata$PM2_5, main='Kolkata')
ts.plot(Mangalore$PM2_5, main='Mangalore')
ts.plot(Mumbai$PM2_5, main='Mumbai')
ts.plot(Mysuru$PM2_5, main='Mysuru')
ts.plot(Nashik$PM2_5, main='Nashik')
ts.plot(Prayagraj$PM2_5, main='Prayagraj')
ts.plot(Puducherry$PM2_5, main='Puducherry')
ts.plot(Pune$PM2_5, main='Pune')
ts.plot(Vijaywada$PM2_5, main='Vijaywada')
ts.plot(Visakhapatnam$PM2_5, main='Visakhapatnam')

#Trend plot for Pune
pune.ts <- ts(Pune$PM2_5, start=2020, freq=365)
time.pts <- c(1:length(pune.ts))
time.pts= c(time.pts- min(time.pts))/max(time.pts)

##Splines Method for Trend Estimation
gam.fit.pm = gam(pune.ts~s(time.pts))
pune.pm.fit.gam = ts(fitted(gam.fit.pm), start=2020, freq=365)

ts.plot(pune.ts,ylab="PM", main="PM Trend")
lines(pune.pm.fit.gam,lwd=2,col="red")

#Not like the others: Asansol
```

#Desert
#CO
```{r}
ts.plot(Agra$CO, main='Agra')
ts.plot(Aurangabad$CO, main='Aurangabad')
ts.plot(Faridabad$CO, main='Faridabad')
ts.plot(Jaipur$CO, main='Jaipur')
ts.plot(Jodhpur$CO, main='Jodhpur')
ts.plot(Kota$CO, main='Kota')
ts.plot(Solapur$CO, main='Solapur')
```


#NO2
```{r}
ts.plot(Agra$NO2, main='Agra')
ts.plot(Aurangabad$NO2, main='Aurangabad')
ts.plot(Faridabad$NO2, main='Faridabad')
ts.plot(Jaipur$NO2, main='Jaipur')
ts.plot(Jodhpur$NO2, main='Jodhpur')
ts.plot(Kota$NO2, main='Kota')
ts.plot(Solapur$NO2, main='Solapur')
```


#SO2
```{r}
ts.plot(Agra$SO2, main='Agra')
ts.plot(Aurangabad$SO2, main='Aurangabad')
ts.plot(Faridabad$SO2, main='Faridabad')
ts.plot(Jaipur$SO2, main='Jaipur')
ts.plot(Jodhpur$SO2, main='Jodhpur')
ts.plot(Kota$SO2, main='Kota')
ts.plot(Solapur$SO2, main='Solapur')

#Not like the others: Kota
```


#PM
```{r}
ts.plot(Agra$PM2_5, main='Agra')
ts.plot(Aurangabad$PM2_5, main='Aurangabad')
ts.plot(Faridabad$PM2_5, main='Faridabad')
ts.plot(Jaipur$PM2_5, main='Jaipur')
ts.plot(Jodhpur$PM2_5, main='Jodhpur')
ts.plot(Kota$PM2_5, main='Kota')
ts.plot(Solapur$PM2_5, main='Solapur')
```

#Subtropic
#CO
```{r}
ts.plot(Aizwal$CO, main='Aizwal')
ts.plot(Amritsar$CO, main='Amritsar')
ts.plot(Bareilly$CO, main='Bareilly')
ts.plot(Chandigarh$CO, main='Chandigarh')
ts.plot(Dehradun$CO, main='Dehradun')
ts.plot(Delhi$CO, main='Delhi')
ts.plot(Ghaziabad$CO, main='Ghaziabad')
ts.plot(Gorakhpur$CO, main='Gorakhpur')
ts.plot(Imphal$CO, main='Imphal')
ts.plot(Jalandhar$CO, main='Jalandhar')
ts.plot(Ludhiana$CO, main='Ludhiana')
ts.plot(Meerut$CO, main='Meerut')
ts.plot(Moradabad$CO, main='Moradabad')
ts.plot(Patna$CO, main='Patna')
ts.plot(Shillong$CO, main='Shillong')
ts.plot(Srinagar$CO, main='Srinagar')
ts.plot(Varanasi$CO, main='Varanasi')

#Not like the others: Aizwal (low variance/low values overall), Shillong
```


#NO2
```{r}
ts.plot(Aizwal$NO2, main='Aizwal')
ts.plot(Amritsar$NO2, main='Amritsar')
ts.plot(Bareilly$NO2, main='Bareilly')
ts.plot(Chandigarh$NO2, main='Chandigarh')
ts.plot(Dehradun$NO2, main='Dehradun')
ts.plot(Delhi$NO2, main='Delhi')
ts.plot(Ghaziabad$NO2, main='Ghaziabad')
ts.plot(Gorakhpur$NO2, main='Gorakhpur')
ts.plot(Imphal$NO2, main='Imphal')
ts.plot(Jalandhar$NO2, main='Jalandhar')
ts.plot(Ludhiana$NO2, main='Ludhiana')
ts.plot(Meerut$NO2, main='Meerut')
ts.plot(Moradabad$NO2, main='Moradabad')
ts.plot(Patna$NO2, main='Patna')
ts.plot(Shillong$NO2, main='Shillong')
ts.plot(Srinagar$NO2, main='Srinagar')
ts.plot(Varanasi$NO2, main='Varanasi')
```


#SO2
```{r}
ts.plot(Aizwal$SO2, main='Aizwal')
ts.plot(Amritsar$SO2, main='Amritsar')
ts.plot(Bareilly$SO2, main='Bareilly')
ts.plot(Chandigarh$SO2, main='Chandigarh')
ts.plot(Dehradun$SO2, main='Dehradun')
ts.plot(Delhi$SO2, main='Delhi')
ts.plot(Ghaziabad$SO2, main='Ghaziabad')
ts.plot(Gorakhpur$SO2, main='Gorakhpur')
ts.plot(Imphal$SO2, main='Imphal')
ts.plot(Jalandhar$SO2, main='Jalandhar')
ts.plot(Ludhiana$SO2, main='Ludhiana')
ts.plot(Meerut$SO2, main='Meerut')
ts.plot(Moradabad$SO2, main='Moradabad')
ts.plot(Patna$SO2, main='Patna')
ts.plot(Shillong$SO2, main='Shillong')
ts.plot(Srinagar$SO2, main='Srinagar')
ts.plot(Varanasi$SO2, main='Varanasi')

#Many SO2 values aren't quite the same

```


#PM
```{r}
ts.plot(Aizwal$PM2_5, main='Aizwal')
ts.plot(Amritsar$PM2_5, main='Amritsar')
ts.plot(Bareilly$PM2_5, main='Bareilly')
ts.plot(Chandigarh$PM2_5, main='Chandigarh')
ts.plot(Dehradun$PM2_5, main='Dehradun')
ts.plot(Delhi$PM2_5, main='Delhi')
ts.plot(Ghaziabad$PM2_5, main='Ghaziabad')
ts.plot(Gorakhpur$PM2_5, main='Gorakhpur')
ts.plot(Imphal$PM2_5, main='Imphal')
ts.plot(Jalandhar$PM2_5, main='Jalandhar')
ts.plot(Ludhiana$PM2_5, main='Ludhiana')
ts.plot(Meerut$PM2_5, main='Meerut')
ts.plot(Moradabad$PM2_5, main='Moradabad')
ts.plot(Patna$PM2_5, main='Patna')
ts.plot(Shillong$PM2_5, main='Shillong')
ts.plot(Srinagar$PM2_5, main='Srinagar')
ts.plot(Varanasi$PM2_5, main='Varanasi')

#Outlier in Ghaziabad
#Srinagar not like others
```
#Meditteran
#CO
```{r}
ts.plot(Bhopal$CO, main='Bhopal')
ts.plot(Gwalior$CO, main='Gwalior')
ts.plot(Jabalpur$CO, main='Jabalpur')
ts.plot(Kanpur$CO, main='Kanpur')
ts.plot(Lucknow$CO, main='Lucknow')
```

#NO2
```{r}
ts.plot(Bhopal$NO2, main='Bhopal')
ts.plot(Gwalior$NO2, main='Gwalior')
ts.plot(Jabalpur$NO2, main='Jabalpur')
ts.plot(Kanpur$NO2, main='Kanpur')
ts.plot(Lucknow$NO2, main='Lucknow')
```

#SO2
```{r}
ts.plot(Bhopal$SO2, main='Bhopal')
ts.plot(Gwalior$SO2, main='Gwalior')
ts.plot(Jabalpur$SO2, main='Jabalpur')
ts.plot(Kanpur$SO2, main='Kanpur')
ts.plot(Lucknow$SO2, main='Lucknow')
```

#PM
```{r}
ts.plot(Bhopal$PM2_5, main='Bhopal')
ts.plot(Gwalior$PM2_5, main='Gwalior')
ts.plot(Jabalpur$PM2_5, main='Jabalpur')
ts.plot(Kanpur$PM2_5, main='Kanpur')
ts.plot(Lucknow$PM2_5, main='Lucknow')
```
#Oceaninc Highland
#CO
```{r}
ts.plot(Gangtok$CO, main='Gangtok')
ts.plot(Kohima$CO, main='Kohima')

```

#NO2
```{r}
ts.plot(Gangtok$NO2, main='Gangtok')
ts.plot(Kohima$NO2, main='Kohima')
```

#SO2
```{r}
ts.plot(Gangtok$SO2, main='Gangtok')
ts.plot(Kohima$SO2, main='Kohima')
```

#PM
```{r}
ts.plot(Gangtok$PM2_5, main='Gangtok')
ts.plot(Kohima$PM2_5, main='Kohima')
```



#Monsoon
#CO
```{r}
ts.plot(Kochi$CO, main='Kochi')
ts.plot(Kozhikode$CO, main='Kozhikode')
ts.plot(Thiruvananthapuram$CO, main='Thiruvananthapuram')
```

#NO2
```{r}
ts.plot(Kochi$NO2, main='Kochi')
ts.plot(Kozhikode$NO2, main='Kozhikode')
ts.plot(Thiruvananthapuram$NO2, main='Thiruvananthapuram')
```


#SO2
```{r}
ts.plot(Kochi$SO2, main='Kochi')
ts.plot(Kozhikode$SO2, main='Kozhikode')
ts.plot(Thiruvananthapuram$SO2, main='Thiruvananthapuram')
```


#PM
```{r}
ts.plot(Kochi$PM2_5, main='Kochi')
ts.plot(Kozhikode$PM2_5, main='Kozhikode')
ts.plot(Thiruvananthapuram$PM2_5, main='Thiruvananthapuram')
```
#Reset dfs if needed
```{r}
#Savannah
df_sav <- rbind(Agartala,Asansol,Belgaum,Bengaluru,Bhilai,Chennai,Coimbatore,Hyderabad,Indore,Kolkata,Mangalore,Mumbai,Mysuru,Nashik,Prayagraj,Puducherry,Pune,Vijaywada,Visakhapatnam)

#Desert
df_desert <- rbind(Agra,Aurangabad,Faridabad,Gandhinagar,Jaipur,Jodhpur,Kota,Solapur)

#Subtropical
df_subtrop <- rbind(Aizwal,Amritsar,Bareilly,Chandigarh,Dehradun,Delhi,Ghaziabad,Gorakhpur,Imphal,Jalandhar,Ludhiana,Meerut,Moradabad,Patna,Shillong,Srinagar,Varanasi)

#Mediterran
df_med <- rbind(Bhopal,Gwalior,Jabalpur,Kanpur,Lucknow)

#Oceanic Highland
df_highland <- rbind(Gangtok,Kohima)

#Monsoon
df_monsoon <- rbind(Kochi, Kozhikode, Thiruvananthapuram)
```

#Import Library
```{r}
library(zoo)
library(lubridate)
library(mgcv)
library(TSA)
library(dynlm)
```



#Aggregate city clusters by day
```{r}
#Savannah
df_sav$Date <- strptime(as.character(df_sav$Date), "%Y-%m-%d")
df_sav$Date <- format(df_sav$Date, "%Y-%m-%d")
df_sav <- df_sav[,-1:-4]
df_sav <- aggregate(x = cbind(df_sav$CO, df_sav$NO2, df_sav$SO2, df_sav$PM2_5), by = list(df_sav$Date), FUN = mean)
colnames(df_sav) <- c("DATE", "CO", "NO2", "SO2", "PM2_5")

#Desert
df_desert$Date <- strptime(as.character(df_desert$Date), "%Y-%m-%d")
df_desert$Date <- format(df_desert$Date, "%Y-%m-%d")
df_desert <- df_desert[,-1:-4]
df_desert <- aggregate(x = cbind(df_desert$CO, df_desert$NO2, df_desert$SO2, df_desert$PM2_5), by = list(df_desert$Date), FUN = mean)
colnames(df_desert) <- c("DATE", "CO", "NO2", "SO2", "PM2_5")

#Subtropic
df_subtrop$Date <- strptime(as.character(df_subtrop$Date), "%Y-%m-%d")
df_subtrop$Date <- format(df_subtrop$Date, "%Y-%m-%d")
df_subtrop <- df_subtrop[,-1:-4]
df_subtrop <- aggregate(x = cbind(df_subtrop$CO, df_subtrop$NO2, df_subtrop$SO2, df_subtrop$PM2_5), by = list(df_subtrop$Date), FUN = mean)
colnames(df_subtrop) <- c("DATE", "CO", "NO2", "SO2", "PM2_5")

#Oceanic Highland
df_highland$Date <- strptime(as.character(df_highland$Date), "%Y-%m-%d")
df_highland$Date <- format(df_highland$Date, "%Y-%m-%d")
df_highland <- df_highland[,-1:-4]
df_highland <- aggregate(x = cbind(df_highland$CO, df_highland$NO2, df_highland$SO2, df_highland$PM2_5), by = list(df_highland$Date), FUN = mean)
colnames(df_highland) <- c("DATE", "CO", "NO2", "SO2", "PM2_5")

#Mediterran
df_med$Date <- strptime(as.character(df_med$Date), "%Y-%m-%d")
df_med$Date <- format(df_med$Date, "%Y-%m-%d")
df_med <- df_med[,-1:-4]
df_med <- aggregate(x = cbind(df_med$CO, df_med$NO2, df_med$SO2, df_med$PM2_5), by = list(df_med$Date), FUN = mean)
colnames(df_med) <- c("DATE", "CO", "NO2", "SO2", "PM2_5")

#Monsoon
df_monsoon$Date <- strptime(as.character(df_monsoon$Date), "%Y-%m-%d")
df_monsoon$Date <- format(df_monsoon$Date, "%Y-%m-%d")
df_monsoon <- df_monsoon[,-1:-4]
df_monsoon <- aggregate(x = cbind(df_monsoon$CO, df_monsoon$NO2, df_monsoon$SO2, df_monsoon$PM2_5), by = list(df_monsoon$Date), FUN = mean)
colnames(df_monsoon) <- c("DATE", "CO", "NO2", "SO2", "PM2_5")
```


#Exploratory Data Analysis

#Savannah
```{r}
sav.co <- ts(df_sav$CO,start=2020, freq=365)
sav.no <- ts(df_sav$NO2,start=2020, freq=365)
sav.so <- ts(df_sav$SO2,start=2020, freq=365)
sav.pm <- ts(df_sav$PM2_5,start=2020, freq=365)

ts.plot(sav.co)
ts.plot(sav.no)
ts.plot(sav.so)
ts.plot(sav.pm)
```

#Desert
```{r}
des.co <- ts(df_desert$CO,start=2020, freq=365)
des.no <- ts(df_desert$NO2,start=2020, freq=365)
des.so <- ts(df_desert$SO2,start=2020, freq=365)
des.pm <- ts(df_desert$PM2_5,start=2020, freq=365)

ts.plot(des.co)
ts.plot(des.no)
ts.plot(des.so)
ts.plot(des.pm)
```

#Subtropical
```{r}
subtrop.co <- ts(df_subtrop$CO,start=2020, freq=365)
subtrop.no <- ts(df_subtrop$NO2,start=2020, freq=365)
subtrop.so <- ts(df_subtrop$SO2,start=2020, freq=365)
subtrop.pm <- ts(df_subtrop$PM2_5,start=2020, freq=365)

ts.plot(subtrop.co)
ts.plot(subtrop.no)
ts.plot(subtrop.so)
ts.plot(subtrop.pm)
```

#Meditteran
```{r}
med.co <- ts(df_med$CO,start=2020, freq=365)
med.no <- ts(df_med$NO2,start=2020, freq=365)
med.so <- ts(df_med$SO2,start=2020, freq=365)
med.pm <- ts(df_med$PM2_5,start=2020, freq=365)

ts.plot(med.co)
ts.plot(med.no)
ts.plot(med.so)
ts.plot(med.pm)
```

#Oceanic Highland
```{r}
highland.co <- ts(df_highland$CO,start=2020, freq=365)
highland.no <- ts(df_highland$NO2,start=2020, freq=365)
highland.so <- ts(df_highland$SO2,start=2020, freq=365)
highland.pm <- ts(df_highland$PM2_5,start=2020, freq=365)

ts.plot(highland.co)
ts.plot(highland.no)
ts.plot(highland.so)
ts.plot(highland.pm)
```

#Monsoon
```{r}
monsoon.co <- ts(df_monsoon$CO,start=2020, freq=365)
monsoon.no <- ts(df_monsoon$NO2,start=2020, freq=365)
monsoon.so <- ts(df_monsoon$SO2,start=2020, freq=365)
monsoon.pm <- ts(df_monsoon$PM2_5,start=2020, freq=365)

ts.plot(monsoon.co)
ts.plot(monsoon.no)
ts.plot(monsoon.so)
ts.plot(monsoon.pm)
```

#Trend and Seasonality Estimation

#Savannah
```{r}
sav.time.pts <- c(1:length(sav.co))
sav.time.pts= c(sav.time.pts- min(sav.time.pts))/max(sav.time.pts)

##Splines Method for Trend Estimation
#CO
gam.fit.co = gam(sav.co~s(sav.time.pts))
sav.co.fit.gam = ts(fitted(gam.fit.co))

#NO2
gam.fit.no = gam(sav.no~s(sav.time.pts))
sav.no.fit.gam = ts(fitted(gam.fit.no))


#SO2
gam.fit.so = gam(sav.so~s(sav.time.pts))
sav.so.fit.gam = ts(fitted(gam.fit.so))

#PM
gam.fit.pm = gam(sav.pm~s(sav.time.pts))
sav.pm.fit.gam = ts(fitted(gam.fit.pm))

#Plots for Trend Estimation
par(mfrow=c(2,2))
ts.plot(df_sav$CO,ylab="CO")
lines(sav.co.fit.gam,lwd=2,col="red")

ts.plot(df_sav$NO2,ylab="NO2")
lines(sav.no.fit.gam,lwd=2,col="red")

ts.plot(df_sav$SO2,ylab="SO2")
lines(sav.so.fit.gam,lwd=2,col="red")

ts.plot(df_sav$PM2_5,ylab="PM")
lines(sav.pm.fit.gam,lwd=2,col="red")

#MAPE for Each model
#CO
mean(abs(df_sav$CO-sav.co.fit.gam)/df_sav$CO)
#NO2
mean(abs(df_sav$NO2-sav.no.fit.gam)/df_sav$NO2)
#SO2
mean(abs(df_sav$SO2-sav.so.fit.gam)/df_sav$SO2)
#PM
mean(abs(df_sav$PM2_5-sav.pm.fit.gam)/df_sav$PM2_5)

```
```{r}

#Trend and Seasonality Estimation

#Parametric
x1<-sav.time.pts
x2<-sav.time.pts**2

#CO
modp.co<-lm(sav.co~x1+x2+season(sav.co))

#NO2
modp.no<-lm(sav.no~x1+x2+season(sav.no))

#SO2
modp.so<-lm(sav.so~x1+x2+season(sav.so))

#PM
modp.pm<-lm(sav.pm~x1+x2+season(sav.pm))
#Plots for Trend and Seasonality Estimation - Parametric Model
par(mfrow=c(2,2))
ts.plot(df_sav$CO,ylab="CO")
lines(fitted(modp.co),lwd=2,col="red")

ts.plot(df_sav$NO2,ylab="NO2")
lines(fitted(modp.no),lwd=2,col="red")

ts.plot(df_sav$SO2,ylab="SO2")
lines(fitted(modp.so),lwd=2,col="red")

ts.plot(df_sav$PM2_5,ylab="PM")
lines(fitted(modp.pm),lwd=2,col="red")


#Nonparametric
#CO
modelnp.co<-gam(sav.co~s(sav.time.pts)+season(sav.co))

#NO2
modelnp.no<-gam(sav.no~s(sav.time.pts)+season(sav.no))

#SO2
modelnp.so<-gam(sav.so~s(sav.time.pts)+season(sav.so))

#PM
modelnp.pm<-gam(sav.pm~s(sav.time.pts)+season(sav.pm))

#Plots for Trend and Seasonality Estimation - Non-Parametric Model
par(mfrow=c(2,2))
ts.plot(df_sav$CO,ylab="CO")
lines(fitted(modelnp.co),lwd=2,col="red")

ts.plot(df_sav$NO2,ylab="NO2")
lines(fitted(modelnp.no),lwd=2,col="red")

ts.plot(df_sav$SO2,ylab="SO2")
lines(fitted(modelnp.so),lwd=2,col="red")

ts.plot(df_sav$PM2_5,ylab="PM")
lines(fitted(modelnp.pm),lwd=2,col="red")

#MAPE Parametric
#CO
mean(abs(df_sav$CO-fitted(modp.co))/df_sav$CO)
#NO2
mean(abs(df_sav$NO2-fitted(modp.no))/df_sav$NO2)
#SO2
mean(abs(df_sav$SO2-fitted(modp.so))/df_sav$SO2)
#PM
mean(abs(df_sav$PM2_5-fitted(modp.pm))/df_sav$PM2_5)

#MAPE Non-Parametric
#CO
mean(abs(df_sav$CO-fitted(modelnp.co))/df_sav$CO)
#NO2
mean(abs(df_sav$NO2-fitted(modelnp.no))/df_sav$NO2)
#SO2
mean(abs(df_sav$SO2-fitted(modelnp.so))/df_sav$SO2)
#PM
mean(abs(df_sav$PM2_5-fitted(modelnp.pm))/df_sav$PM2_5)

```



#Desert
```{r}
des.time.pts <- c(1:length(des.co))
des.time.pts= c(des.time.pts- min(des.time.pts))/max(des.time.pts)

#CO
gam.fit.co = gam(des.co~s(des.time.pts))
des.co.fit.gam = ts(fitted(gam.fit.co))

#NO2
gam.fit.no = gam(des.no~s(des.time.pts))
des.no.fit.gam = ts(fitted(gam.fit.no))


#SO2
gam.fit.so = gam(des.so~s(des.time.pts))
des.so.fit.gam = ts(fitted(gam.fit.so))

#PM
gam.fit.pm = gam(des.pm~s(des.time.pts))
des.pm.fit.gam = ts(fitted(gam.fit.pm))

#Plots
par(mfrow=c(2,2))
ts.plot(df_desert$CO,ylab="CO")
lines(des.co.fit.gam,lwd=2,col="red")

ts.plot(df_desert$NO2,ylab="SO2")
lines(des.no.fit.gam,lwd=2,col="red")

ts.plot(df_desert$SO2,ylab="SO2")
lines(des.so.fit.gam,lwd=2,col="red")

ts.plot(df_desert$PM2_5,ylab="SO2")
lines(des.pm.fit.gam,lwd=2,col="red")
```

#Subtropical
```{r}
sub.time.pts <- c(1:length(subtrop.co))
sub.time.pts= c(sub.time.pts- min(sub.time.pts))/max(sub.time.pts)

##Splines Method for Trend Estimation
#CO
gam.fit.co = gam(subtrop.co~s(sub.time.pts))
sub.co.fit.gam = ts(fitted(gam.fit.co))

#NO2
gam.fit.no = gam(subtrop.no~s(sub.time.pts))
sub.no.fit.gam = ts(fitted(gam.fit.no))


#SO2
gam.fit.so = gam(subtrop.so~s(sub.time.pts))
sub.so.fit.gam = ts(fitted(gam.fit.so))

#PM
gam.fit.pm = gam(subtrop.pm~s(sub.time.pts))
sub.pm.fit.gam = ts(fitted(gam.fit.pm))

#Plots
par(mfrow=c(2,2))
ts.plot(df_subtrop$CO,ylab="CO")
lines(sub.co.fit.gam,lwd=2,col="red")

ts.plot(df_subtrop$NO2,ylab="SO2")
lines(sub.no.fit.gam,lwd=2,col="red")

ts.plot(df_subtrop$SO2,ylab="SO2")
lines(sub.so.fit.gam,lwd=2,col="red")

ts.plot(df_subtrop$PM2_5,ylab="SO2")
lines(sub.pm.fit.gam,lwd=2,col="red")
```

#Mediterran
```{r}
med.time.pts <- c(1:length(med.co))
med.time.pts= c(med.time.pts- min(med.time.pts))/max(med.time.pts)

##Splines Method for Trend Estimation
#CO
gam.fit.co = gam(med.co~s(med.time.pts))
med.co.fit.gam = ts(fitted(gam.fit.co))

#NO2
gam.fit.no = gam(med.no~s(med.time.pts))
med.no.fit.gam = ts(fitted(gam.fit.no))

#SO2
gam.fit.so = gam(med.so~s(med.time.pts))
med.so.fit.gam = ts(fitted(gam.fit.so))

#PM
gam.fit.pm = gam(med.pm~s(med.time.pts))
med.pm.fit.gam = ts(fitted(gam.fit.pm))

#Plots
par(mfrow=c(2,2))
ts.plot(df_med$CO,ylab="CO")
lines(med.co.fit.gam,lwd=2,col="red")

ts.plot(df_med$NO2,ylab="SO2")
lines(med.no.fit.gam,lwd=2,col="red")

ts.plot(df_med$SO2,ylab="SO2")
lines(med.so.fit.gam,lwd=2,col="red")

ts.plot(df_med$PM2_5,ylab="SO2")
lines(med.pm.fit.gam,lwd=2,col="red")
```

#Highland
```{r}
highland.time.pts <- c(1:length(highland.co))
highland.time.pts= c(highland.time.pts- min(highland.time.pts))/max(highland.time.pts)

##Splines Method for Trend Estimation
#CO
gam.fit.co = gam(highland.co~s(highland.time.pts))
highland.co.fit.gam = ts(fitted(gam.fit.co))

#NO2
gam.fit.no = gam(highland.no~s(highland.time.pts))
highland.no.fit.gam = ts(fitted(gam.fit.no))


#SO2
gam.fit.so = gam(highland.so~s(highland.time.pts))
highland.so.fit.gam = ts(fitted(gam.fit.so))

#PM
gam.fit.pm = gam(highland.pm~s(sav.time.pts))
highland.pm.fit.gam = ts(fitted(gam.fit.pm))

#Plots
par(mfrow=c(2,2))
ts.plot(df_highland$CO,ylab="CO")
lines(highland.co.fit.gam,lwd=2,col="red")

ts.plot(df_highland$NO2,ylab="SO2")
lines(highland.no.fit.gam,lwd=2,col="red")

ts.plot(df_highland$SO2,ylab="SO2")
lines(highland.so.fit.gam,lwd=2,col="red")

ts.plot(df_highland$PM2_5,ylab="SO2")
lines(highland.pm.fit.gam,lwd=2,col="red")
```

#Monsoon
```{r}
monsoon.time.pts <- c(1:length(monsoon.co))
monsoon.time.pts= c(monsoon.time.pts- min(monsoon.time.pts))/max(monsoon.time.pts)

##Splines Method for Trend Estimation
#CO
gam.fit.co = gam(monsoon.co~s(monsoon.time.pts))
monsoon.co.fit.gam = ts(fitted(gam.fit.co))

#NO2
gam.fit.no = gam(monsoon.no~s(monsoon.time.pts))
monsoon.no.fit.gam = ts(fitted(gam.fit.no))


#SO2
gam.fit.so = gam(monsoon.so~s(monsoon.time.pts))
monsoon.so.fit.gam = ts(fitted(gam.fit.so))

#PM
gam.fit.pm = gam(monsoon.pm~s(monsoon.time.pts))
monsoon.pm.fit.gam = ts(fitted(gam.fit.pm))

#Plots
par(mfrow=c(2,2))
ts.plot(df_monsoon$CO,ylab="CO")
lines(monsoon.co.fit.gam,lwd=2,col="red")

ts.plot(df_monsoon$NO2,ylab="SO2")
lines(monsoon.no.fit.gam,lwd=2,col="red")

ts.plot(df_monsoon$SO2,ylab="SO2")
lines(monsoon.so.fit.gam,lwd=2,col="red")

ts.plot(df_monsoon$PM2_5,ylab="SO2")
lines(monsoon.pm.fit.gam,lwd=2,col="red")
```









